%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[grey]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
% customizing link colors and formatting
\hypersetup{colorlinks=true}
%\hypersetup{a4paper=true}
\usepackage{color}
\definecolor{iorange}{RGB}{243,110,36}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%PERSONAL DATA%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% personal data
\firstname{Anuja}
\familyname{Tupe}
\title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{\hspace{-1in}Plot no. 116, Amar Cottages,\\Bhosale Nagar,Hadapsar}{Pune, 411028}    % optional, remove the line if not wanted
\mobile{mobile +91-9762801386}                    % optional, remove the line if not wanted
%\phone{}                      % optional, remove the line if not wanted
\email{anujatupe2012@gmail.com}                      % optional, remove the line if not wanted
\extrainfo{GitHub: github.com/anujatupe}
%\extrainfo{ }        

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%EDUCATION%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\cventry{2008-2012}{Bachelor of engineering in Computer Science}{}{University of Pune}{India}{Studied at All India Shri Shivaji Memorial Society's College of Engineering. Secured distinction till date (66.86\%). Graduated in end-July, 2012.}  
\cventry{2007-2008}{HSC}{MSBSHSE}{Pune}{IN}{Studied at Fergusson College, Pune. Secured 88.67\%}  % arguments 3 to 6 are optional
\cventry{2005-2006}{SSC}{MSBSHSE}{Pune}{IN}{Studied at St. Anne's High School, Pune. Secured 92.66\%.}  % arguments 3 to 6 are optional

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%TECHNICAL SKILLS%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cvcomputer{}{} {}{}

\vspace{.4in}\section{Technical Skills} 
\cvcomputer{\textbf{Platforms}}{GNU/Linux(Ubuntu,Fedora,Mint),\\Microsoft\textsuperscript{\textregistered} Windows\textsuperscript{\textregistered}.}{\textbf{Programming Languages Used}}{C: Intermediate, \\C++: Intermediate,\\ Java: Beginner, \\ Python:Beginner. \\ } {}{}
\cvcomputer{\textbf{Frameworks}}{Microsoft\textsuperscript{\textregistered} Visual Studio\textsuperscript{\textregistered} }{\textbf{Development Tools}}{Vim, Git, LaTeX.}
\cvcomputer{\textbf{Databases}}{Oracle, MySQL}  {\textbf{}}{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%EXPERIENCE%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
%IDPS(SVM)
\cventry
{2011-2012}
{Intrusion Detection and Prevention System(SVM)}
{Final year engineering project}
{}
{}
{Network Intrusion Detection and Prevention System using
Support Vector Machine (SVM).An attempt to overcome the limitations present in using other intrusion detection methods like pattern recognition,rule based techniques etc. by using Support Vector machine algorithm.Currently an offline project.The entire project is coded in Java version 1.7 using Netbeans 7.1 as the IDE.
}


%Banking system
\cventry
{May, 2011}
{Banking system}
{Third year engineering mini-project}
{}
{}
{Project for a Banking system using VB.net and Microsoft Access as database.
}

%Hospital Management System
\cventry
{September, 2010}
{Hospital Management System}
{Third year engineering mini-project}
{}
{}
{As part of the curriculum, created a mini-project for handling and managing records of patients, Doctors and staff in a hospital using VB, Microsoft Access. }

\newpage
\section{Seminars Conducted}



\cventry
{May 2011}
{An overview of security concerns in the enterprise cloud computing}
{}
{}
{}
{Presented this seminar to show the security concerns in cloud computing as a part of curriculum.}

\cventry
{September 2009}
{Basics of VHDL}
{}
{}
{}
{Presented this seminar as an activity for the Computer Society India branch of the college.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%Co-Curricular%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Co-Curricular}
\subsection{Talks and Workshops attended}
\cventry{}{* Introduction to Ruby and Ruby on Rails}{}{}{}{}
\cventry{}{* Getting started with Sencha Touch 2}{}{}{}{}	
\cventry{}{* FudCon 2011}{}{}{}{}
\cventry{}{* GNUnify2011, 2012}{}{}{}{}
\cventry{}{* Basics of programming in Python}{}{}{}{}
\cventry{}{* Cloud Computing (Cloud Camp) at Persistent Systems Ltd}{}{}{}{}
\cventry{}{* Workshop on Building Effective websites using DRUPAL (GNUnify)}{}{}{}{}
	


\subsection{Other}
\cventry{}{* Selection of paper titling NNIDPS-Neural Network Based Intrusion Detection with Prevention System at International Conference on Computer Applications (ICCA) 2012, Pondicherry. Rating acquired: 4.47/5.0}{}{}{}{}	
\cventry{}{* Was the chairman of the CSI(Computer Society India) committee of college}{}{}{}{}
\cventry{}{* Participated in College Festivals}{}{}{}{}	
\cventry{}{* Made cartoon posters for college fests and technical events}{}{}{}{}	

\section{Achievements}
\cventry{}{* Merit Holder in the SSC Examination}{}{}{}{}
\cventry{}{* Selection of paper titling NNIDPS-Neural Network Based Intrusion Detection with Prevention System at International Conference on Computer Applications (ICCA) 2012, Pondicherry. Rating acquired: 4.47/5.0}{}{}{}{}	
\cventry{}{* Was the chairman of the CSI committee of college
}{}{}{}{}
\cventry{}{* Had excelled in Karate and attained various belts after appearing for grading tests
(International Federation of Karate-IFK)
}{}{}{}{}


%\cvlistitem{ Item 1}
%\cvlistitem{ Item 2
% \\http://example.com
%  \\http://example2.com}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%INTERESTS & HOBBIES%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section{Interests and Hobbies}
\cvline{Cooking}{\small I love experimenting new delicacies.}
\cvline{Reading}{\small Reading technical books and fictional and non-fiction novels.} 
\cvline{Travelling}{\small I love travelling on weekends.}
\cvline{Drawing}{\small I love drawing and painting.}

\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists
\end{document}

